---
title: "Pilot analysis"
author: "Sau-Chin Chen"
date: "2022/4/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(broom)
library(effectsize)
```

In this document we generated the pseudo data and reproduced the analysis summary as the norming study in [Hoeben Mannaert et al. (2021)](https://link.springer.com/article/10.3758/s13421-020-01078-6#Sec4) (p. 131).


## Data sheet structure

- jatosStudyResultId: by-participant unit
- term: by-item unit

- Design: Pictures are the "critical" objects or "fillers".
- Color_pic: Picture is color (Y) or blank (N).

The two coloums are from "sti_table.csv"

- response_time: Pseudo response time.  
- correct: Pseudo correctness. 

```{r real_data}
## Define system variables
system_cols <- c("browser_codename", "browser_name", "browser_version", "date_startdate", "date_startdateUTC", "date_starttime", "experiment_debug", "experiment_parameters", "experiment_pilot", "experiment_taskname", "experiment_taskversion", "jatosStudyResultId", "jatosVersion", "screen_availableHeight", "screen_availableWidth", "screen_colorDepth", "screen_height", "screen_pixelDepth", "screen_screenX", "screen_screenY", "screen_width", "system_os")

## import real data
df_testing <- read_csv(file="testing_results/jatos_results_20220501065916.csv") %>% left_join(read_csv("sti_table.csv"),by=c("picture","term")) %>%  ## download from osf
  select(-system_cols,"jatosStudyResultId") 

## summary 

df_meta <- read_csv(file = "testing_results/jatos_meta_20220501063856.csv") %>%
  select(c(`Result ID`,"gender","age"))

meta_sum <- df_meta %>% summarise(N = n(), female_N = sum(gender=="f",na.rm=TRUE), age_M = range(age, na.rm=TRUE))

critical_terms <- c("空氣清新劑",
"斧頭","氣球","球棒","腳踏車","小鳥","襯衫","精裝書","碗","椅子","支票簿","寶箱","外套鈕扣","餅乾罐","杯子","羽毛撣子","魚","叉子","手套","錘子","安全帽","刀子","桌燈","緊身褲","口紅","滑鼠墊","記事本","塑膠湯匙","手提包","耙子","電鋸","圍巾","螺絲釘","螺絲起子","鞋子","短褲","裙子","拖鞋","汽水罐","沙發","網球拍","桌子","網球拍","牙刷","T恤","雨傘","板手","瑜珈墊")

filler_terms <-c("信用卡","梳子","洗衣籃","蝴蝶","腰帶","蝴蝶","帽子","沙漏","鉛筆","打火機","鏟子","書桌","卡車","毛巾","鑷子","手錶","長笛","夾克","襪子","車子","書籤","支票","剪刀","毛線球","花瓶","盒裝衛生紙","鬧鐘","門板","衣櫃","花朵","錢包","瓶子","巴士","盤子","旗幟","手鐲","原子筆","指甲銼","褲子","枕頭","吉他","被子","小提琴","瓶蓋","衣架","盒子","領帶","郵票")

## extract the exp data
df_norm <- df_testing %>% filter(jatosStudyResultId %in% df_meta$`Result ID`) %>% filter(Task=="Exp")
## extract the memory checks
df_memory <- df_norm %>% filter(memory == "y")
## extract the post survey data
df_post <- df_testing %>% filter(jatosStudyResultId %in% df_meta$`Worker ID`) %>% filter(jatosStudyResultId %in% df_meta$jatosStudyResultId) %>% filter(Task=="Post")


## Extract the terms and picture names from the real data
real_sti <- df_norm %>% select(Design, Color_pic, term, picture) %>% distinct() %>%
  arrange(Design, Color_pic)

#filter(real_sti,Design == "Critical" & Color_pic == "Y") %>% arrange(picture) #48 太陽眼鏡被誤植為網球拍

#filter(real_sti,Design == "Critical" & Color_pic == "N") %>% arrange(picture) #48 太陽眼鏡被誤植為網球拍

#filter(real_sti,Design == "Filler" & Color_pic == "Y") %>% arrange(term) #47

#filter(real_sti,Design == "Filler" & Color_pic == "N") %>% arrange(term) #48

```


This study has `r length(critical_terms)` critical objects which have `r length(critical_terms)` color pictures and `r length(critical_terms)` blank pictures and `r length(filler_terms)` filler objects which have `r length(filler_terms)` color pictures and `r length(filler_terms)` blank pictures. In the real data, the last script recorded `r (filter(real_sti,Design == "Critical" & Color_pic == "Y") %>% dim())[1]` critical objects with color pictures; `r (filter(real_sti,Design == "Critical" & Color_pic == "N") %>% dim())[1]` critical objects with blank pictures; `r (filter(real_sti,Design == "Filler" & Color_pic == "Y") %>% dim())[1]` critical objects with color pictures; `r (filter(real_sti,Design == "Filler" & Color_pic == "N") %>% dim())[1]` critical objects with blank pictures. The missed filler term was "吉他".




## Demographic summary


Totally `r meta_sum$N` participants (`r meta_sum$female_N` females) joined our pilot study, age range: `r paste(meta_sum$age_M, collapse = " - ")` years.

## Making of analytic table

Build the tables for by-participant and by-item t-tests.

```{r by-particiant-table, echo=FALSE}
## for t-test on accuracy
p_Acc <- df_norm %>%
  group_by(jatosStudyResultId, Design, Color_pic) %>%
  summarise(Acc=mean(correct))

## Making of p_table
p_Acc_tb <- p_Acc %>%
  group_by(Design, Color_pic) %>%
  summarise(N = n(), Accuracy = mean(Acc), SD = sd(Acc))

## for t-test on RT
p_RT <- df_norm %>%
  filter(correct==1) %>%
  group_by(jatosStudyResultId, Design, Color_pic) %>%
  summarise(pRT= mean(response_time))


## Making of p_table
p_RT_tb <- p_RT %>%
  group_by(Design, Color_pic) %>%
  summarise(N= n(), mRT = mean(pRT), SD = sd(pRT))

```

Summary by participants

`r knitr::kable(p_RT_tb)`


`r knitr::kable(p_Acc_tb)`

Critical pictures and filler pictures had unequal response times between color version and blank version. Participants' accuracy were lower for critical pictures.

```{r by-item-table, echo=FALSE}


## for t-test on accuracy
i_Acc <- df_norm %>%
  group_by(term, Design, Color_pic) %>%
  summarise(Acc=mean(correct))

#subset(i_Acc, Design == "Critical" & Color_pic == "Y")$term 

#critical_terms

#filler_terms %in% subset(i_Acc, Design == "Filler"& Color_pic == "Y")$term

## Making of i_table
i_Acc_tb <- i_Acc %>%
  group_by(Design, Color_pic) %>%
  summarise(N = n(), Accuracy = mean(Acc), SD = sd(Acc))


## for t-test on RT
i_RT <- df_norm %>%
  filter(correct==1) %>%
  group_by(term, Design, Color_pic) %>%
  summarise(iRT = mean(response_time))

## Making of p_table
i_RT_tb <- i_RT %>%
  group_by(Design, Color_pic) %>%
  summarise(N = n(), mRT = mean(iRT), SD = sd(iRT))
```

Summary by items

`r knitr::kable(i_RT_tb)`


`r knitr::kable(i_Acc_tb)`


We missed one critical picture of "sunglasses" because the term was incorrect (太陽眼鏡).



## T-tests by condition and by measurement

```{r planned_ttest, echo=TRUE}
## by-participant RT analysis 
result_p_Critical_RT <- t.test(pRT ~ Color_pic,
       paired = TRUE,
       data=subset(p_RT,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_p_Filler_RT <- t.test(pRT ~ Color_pic,
       paired = TRUE,
       data=subset(p_RT,Design=="Filler"),
       alternative = "less") %>%
  tidy()

## by-item RT analysis 
result_i_Critical_RT <- t.test(iRT ~ Color_pic,
       paired = TRUE,
       data=subset(i_RT,Design=="Critical"),
       alternative = "less") %>%
  tidy()

## by-participant Accuracy analysis
result_p_Critical_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(p_Acc,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_p_Filler_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(p_Acc,Design=="Filler"),
       alternative = "less") %>%
  tidy()

## by-item Accuracy analysis
result_i_Critical_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(i_Acc,Design=="Critical"),
       alternative = "less") %>%
  tidy()
```


> A paired-samples t test found no significant color advantage  for experimental items: by the response times, $t_1$(`r round(result_p_Critical_RT$parameter, 2)`) = `r round(result_p_Critical_RT$statistic, 2)`, *p* = `r round(result_p_Critical_RT$p.value, 3)`; $t_2$(`r round(result_i_Critical_RT$parameter, 2)`) = `r round(result_i_Critical_RT$statistic, 2)`, *p* = `r round(result_i_Critical_RT$p.value, 3)`, and by the accuracy, $t_1$(`r round(result_p_Critical_Acc$parameter, 2)`) = `r round(result_p_Critical_Acc$statistic, 2)`, *p* = `r round(result_p_Critical_Acc$p.value, 3)`; $t_2$(`r round(result_i_Critical_Acc$parameter, 2)`) = `r round(result_i_Critical_Acc$statistic, 2)`, *p* = `r round(result_i_Critical_Acc$p.value, 3)`.


## Compare item RTs between "color" and "blank"

```{r items}
i_RT_tb <- df_norm %>%
  filter(correct==1) %>%
  group_by(term, Design, Color_pic) %>%
  summarise(iEXC = mean(response_time), iVER = qnorm(.975)*sd(response_time)) # summarise the confidence intervals by item per color

i_RT_tb %>% ggplot(aes(y=term,x=iEXC,xmin=iEXC-iVER, xmax=iEXC+iVER, color = Color_pic)) +
  geom_pointrange() +
  coord_cartesian(expand = FALSE) # Illustrate the ranges of item RT

ggsave(filename = "item_comparision.png")
```

## Exclude strange items

```{r items-filter, echo=TRUE}
strange_items <- c("空氣清新劑","外套鈕扣","牙刷","螺絲起子","被子","網球拍","小提琴","吉他")
df_norm_excluded <- df_norm %>% filter(!(term %in% strange_items))
```

## Analytic table after excluded strange items

Based on the filtered items, we build the tables for by-participant and by-item t-tests.

```{r by-particiant-table-rev, echo=FALSE}
## for t-test on accuracy
p_Acc <- df_norm_excluded %>%
  group_by(jatosStudyResultId, Design, Color_pic) %>%
  summarise(Acc=mean(correct))

## Making of p_table
p_Acc_tb <- p_Acc %>%
  group_by(Design, Color_pic) %>%
  summarise(N = n(), Accuracy = mean(Acc), SD = sd(Acc))

## for t-test on RT
p_RT <- df_norm_excluded %>%
  filter(correct==1) %>%
  group_by(jatosStudyResultId, Design, Color_pic) %>%
  summarise(pRT= mean(response_time))


## Making of p_table
p_RT_tb <- p_RT %>%
  group_by(Design, Color_pic) %>%
  summarise(N= n(), mRT = mean(pRT), SD = sd(pRT))

```

Summary by participants

`r knitr::kable(p_RT_tb)`


`r knitr::kable(p_Acc_tb)`

Critical pictures and filler pictures had unequal response times between color version and blank version. Participants' accuracy were lower for critical pictures.

```{r by-item-table-rev, echo=FALSE}
## for t-test on accuracy
i_Acc <- df_norm_excluded %>%
  group_by(term, Design, Color_pic) %>%
  summarise(Acc=mean(correct))

## Making of i_table
i_Acc_tb <- i_Acc %>%
  group_by(Design, Color_pic) %>%
  summarise(N = n(), Accuracy = mean(Acc), SD = sd(Acc))

## for t-test on RT
i_RT <- df_norm_excluded %>%
  filter(correct==1) %>%
  group_by(term, Design, Color_pic) %>%
  summarise(iRT = mean(response_time))

## Making of p_table
i_RT_tb <- i_RT %>%
  group_by(Design, Color_pic) %>%
  summarise(N = n(), mRT = mean(iRT), SD = sd(iRT))
```

Summary by items

`r knitr::kable(i_RT_tb)`


`r knitr::kable(i_Acc_tb)`



## Rerun T-tests by condition and by measurement

```{r planned_ttest_rev, echo=TRUE}
## by-participant RT analysis 
result_p_Critical_RT <- t.test(pRT ~ Color_pic,
       paired = TRUE,
       data=subset(p_RT,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_p_Filler_RT <- t.test(pRT ~ Color_pic,
       paired = TRUE,
       data=subset(p_RT,Design=="Filler"),
       alternative = "less") %>%
  tidy()

## by-item RT analysis 
result_i_Critical_RT <- t.test(iRT ~ Color_pic,
       paired = TRUE,
       data=subset(i_RT,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_i_Filler_RT <- t.test(iRT ~ Color_pic,
       paired = TRUE,
       data=subset(i_RT,Design=="Filler"),
       alternative = "less") %>%
  tidy()


## by-participant Accuracy analysis
result_p_Critical_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(p_Acc,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_p_Filler_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(p_Acc,Design=="Filler"),
       alternative = "less") %>%
  tidy()

## by-item Accuracy analysis
result_i_Critical_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(i_Acc,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_i_Filler_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(i_Acc,Design=="Filler"),
       alternative = "less") %>%
  tidy()
```


> A paired-samples t test found no significant color advantage for experimental items: by the response times, $t_1$(`r round(result_p_Critical_RT$parameter, 2)`) = `r round(result_p_Critical_RT$statistic, 2)`, *p* = `r round(result_p_Critical_RT$p.value, 3)`; $t_2$(`r round(result_i_Critical_RT$parameter, 2)`) = `r round(result_i_Critical_RT$statistic, 2)`, *p* = `r round(result_i_Critical_RT$p.value, 3)`, and by the accuracy, $t_1$(`r round(result_p_Critical_Acc$parameter, 2)`) = `r round(result_p_Critical_Acc$statistic, 2)`, *p* = `r round(result_p_Critical_Acc$p.value, 3)`; $t_2$(`r round(result_i_Critical_Acc$parameter, 2)`) = `r round(result_i_Critical_Acc$statistic, 2)`, *p* = `r round(result_i_Critical_Acc$p.value, 3)`. Another paired-samples t test found no significant color advantage for filler items: by the response times, $t_1$(`r round(result_p_Filler_RT$parameter, 2)`) = `r round(result_p_Filler_RT$statistic, 2)`, *p* = `r round(result_p_Filler_RT$p.value, 3)`; $t_2$(`r round(result_i_Filler_RT$parameter, 2)`) = `r round(result_i_Filler_RT$statistic, 2)`, *p* = `r round(result_i_Filler_RT$p.value, 3)`, and by the accuracy, $t_1$(`r round(result_p_Filler_Acc$parameter, 2)`) = `r round(result_p_Filler_Acc$statistic, 2)`, *p* = `r round(result_p_Filler_Acc$p.value, 3)`; $t_2$(`r round(result_i_Filler_Acc$parameter, 2)`) = `r round(result_i_Filler_Acc$statistic, 2)`, *p* = `r round(result_i_Filler_Acc$p.value, 3)`.


**Warning** This analysis excluded `r length(strange_items)` items: `r strange_items`.