---
title: "Pilot analysis"
author: "Sau-Chin Chen"
date: "2022/4/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(broom)
library(effectsize)
```

## Data sheet structure

- ID: by-participant unit
- term: by-item unit

- Design:
- Color_pic:

- RT:
- Correct: 

```{r build_data_sheet}
df <- tibble(
  ID = paste0("s",rep(1:39,each=96*2)),
  gender=rep(c("Female","Male"),c(96*2*35,96*2*4)),
  age=rep(sample(17:26,size=39,replace = TRUE,prob = c(rep(0.15,6),rep(0.1/4,4))),each=96*2),
  Color_pic	= rep(rep(rep(c("Y","N"),each=48),2),39),
  Design = rep(rep(c("Critical","Filler"),each=96),39),
  term = rep(paste0("i",c(rep(1:48,2),rep(49:96,2))),39),
  RT = c(replicate(4*39,round(rnorm(48,500,10),0) )),
  Correct = c(replicate(4*39,sample(0:1,size = 48,replace = TRUE,prob=c(.01,.99)) ))
)

## count how many female participants
femaleN <- df %>% filter(gender=="Female") %>% summarise(N = length(unique(ID)) ) %>% pull(N)

## count the range of ages
age_range <- df %>% summarise(ages = range(age)) %>% pull(ages)
```


## Demographic summary

In the simulated data, there are __ female participants, age range: __ years.


## Making of analytic table

Build the tables for by-participant and by-item t-tests.

```{r by-particiant-table, echo=FALSE}
## for t-test on accuracy
p_Acc <- df %>%
  group_by(ID, Design, Color_pic) %>%
  summarise(Acc=mean(Correct))

## Making of p_table
p_Acc_tb <- p_Acc %>%
  group_by(Design, Color_pic) %>%
  summarise(Accuracy = mean(Acc))

## for t-test on RT
p_RT <- df %>%
  filter(Correct==1) %>%
  group_by(ID, Design, Color_pic) %>%
  summarise(pRT= mean(RT))


## Making of p_table
p_RT_tb <- p_RT %>%
  group_by(Design, Color_pic) %>%
  summarise(mRT = mean(pRT))

```

Summary by participants

`r knitr::kable(p_RT_tb)`


`r knitr::kable(p_Acc_tb)`

```{r by-item-table, echo=FALSE}
## for t-test on accuracy
i_Acc <- df %>%
  group_by(term, Design, Color_pic) %>%
  summarise(Acc=mean(Correct))

## Making of i_table
i_Acc_tb <- i_Acc %>%
  group_by(Design, Color_pic) %>%
  summarise(Accuracy = mean(Acc))


## for t-test on RT
i_RT <- df %>%
  filter(Correct==1) %>%
  group_by(term, Design, Color_pic) %>%
  summarise(iRT = mean(RT))

## Making of p_table
i_RT_tb <- i_RT %>%
  group_by(Design, Color_pic) %>%
  summarise(mRT = mean(iRT))
```

Summary by items

`r knitr::kable(i_RT_tb)`


`r knitr::kable(i_Acc_tb)`


## T-tests by condition and by measurement

```{r planned_ttest, echo=FALSE}
## by-participant RT analysis 
result_p_Critical_RT <- t.test(pRT ~ Color_pic,
       paired = TRUE,
       data=subset(p_RT,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_p_Filler_RT <- t.test(pRT ~ Color_pic,
       paired = TRUE,
       data=subset(p_RT,Design=="Filler"),
       alternative = "less") %>%
  tidy()

## by-item RT analysis 
result_i_Critical_RT <- t.test(iRT ~ Color_pic,
       paired = TRUE,
       data=subset(i_RT,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_i_Filler_RT <- t.test(iRT ~ Color_pic,
       paired = TRUE,
       data=subset(i_RT,Design=="Filler"),
       alternative = "less") %>%
  tidy()



## by-participant Accuracy analysis
result_p_Critical_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(p_Acc,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_p_Filler_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(p_Acc,Design=="Filler"),
       alternative = "less") %>%
  tidy()

## by-item Accuracy analysis
result_i_Critical_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(i_Acc,Design=="Critical"),
       alternative = "less") %>%
  tidy()

result_i_Filler_Acc <- t.test(Acc ~ Color_pic,
       paired = TRUE,
       data=subset(i_Acc,Design=="Filler"),
       alternative = "less") %>%
  tidy()

```

In this document we generated the simulated data and reproduced the analysis summary as Hoeben Mannaert et al. ( 2021) on p. 131.

> A paired-samples t test found no significant color advantage in the response times for either experimental items, $t_1$(`r round(result_p_Critical_RT$parameter, 2)`) = `r round(result_p_Critical_RT$statistic, 2)`, *p* = `r round(result_p_Critical_RT$p.value, 3)`; $t_2$(`r round(result_i_Critical_RT$parameter, 2)`) = `r round(result_i_Critical_RT$statistic, 2)`, *p* = `r round(result_i_Critical_RT$p.value, 3)`, or for filler items,  $t_1$(`r round(result_p_Filler_RT$parameter, 2)`) = `r round(result_p_Filler_RT$statistic, 2)`, *p* = `r round(result_p_Filler_RT$p.value, 3)`; $t_2$(`r round(result_i_Filler_RT$parameter, 2)`) = `r round(result_i_Filler_RT$statistic, 2)`, *p* = `r round(result_i_Filler_RT$p.value, 3)`. (Cotinue to Accuracy analysis)
