---
title: "Review Prolific data"
author: "Sau-Chin Chen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Load prolific meta data


```{r EC-prolific-meta}
EC_prolific_meta <- read_csv("EC_prolific_approved_export_641bb22edafdb9baaae4d584.csv")
```

```{r CE-prolific-meta}
CE_prolific_meta <- read_csv("CE_prolific_approved_export_641bb2543ae0d27e600659f5.csv")
```


## Load jatos/mindprobe data files


```{r EC-jatos-data}
EC_jatos_data <- read_csv("EC_jatos_results_data_20230331223738.csv")
```

```{r CE-jatos-data}
CE_jatos_data <- read_csv("CE_jatos_results_data_20230331224753.csv")
```

## Match the completion codes


### EC group

```{r EC-match}
EC_checks <- EC_prolific_meta %>% select(`Participant id`,`Completion code`) %>%
left_join(
EC_jatos_data %>% select(prolific_participant_id,identifier) %>%
  distinct(),
by=(c(`Participant id` = "prolific_participant_id"))
) %>% 
  mutate(Match = if_else(`Completion code`==identifier,"Yes","No"))

## Retrieve the approved participants' id
#writeClipboard(EC_checks %>% filter(Match == "Yes") %>% pull(`Participant id`) )
```

`r sum(!is.na(EC_checks$Match))` participants had the completion code at the end. `r sum(EC_checks$Match == "Yes",na.rm=TRUE)` participants successfully provided their completion code.

`r EC_checks%>% knitr::kable()`


### CE group

```{r CE-match}
CE_checks <- CE_prolific_meta %>% select(`Participant id`,`Completion code`) %>%
left_join(
CE_jatos_data %>% select(prolific_participant_id,identifier) %>%
  distinct(),
by=(c(`Participant id` = "prolific_participant_id"))
) %>% 
  mutate(Match = if_else(`Completion code`==identifier,"Yes","No")) 

## Retrieve the approved participants' id
writeClipboard(CE_checks %>% filter(Match == "Yes") %>% pull(`Participant id`) )
```

`r sum(!is.na(CE_checks$Match))` participants had the completion code at the end. `r sum(CE_checks$Match == "Yes",na.rm=TRUE)` participants successfully provided their completion code.

`r CE_checks%>% knitr::kable()`

## Summarize the data tables


### EC group

```{r EC-filtered-data}
EC_jatos_data %>% filter(prolific_participant_id %in% (subset(EC_checks,!is.na(identifier)) %>% pull(`Participant id`))) %>% 
select("Level", "Q_id", "Question", "birth_year", "correct", "ctest_file", "date_startdate", "date_startdateUTC", "date_starttime", "gender_code", "identifier", "jatosStudyResultId", "jatosVersion", "lang_code", "prolific_participant_id", "prolific_session_id", "prolific_study_id", "response", "response_clang", "screen_availableHeight", "screen_availableWidth", "screen_colorDepth", "screen_height", "screen_pixelDepth", "screen_screenX", "screen_screenY", "screen_width", "system_os", "test_file", "test_topic") %>% 
  write_csv(file = "EC_pilot_rawdata.csv")
```



### CE group

```{r CE-filtered-data}
CE_jatos_data %>% filter(prolific_participant_id %in% (subset(CE_checks,!is.na(identifier)) %>% pull(`Participant id`))) %>% 
select("Level", "Q_id", "Question", "birth_year", "correct", "ctest_file", "date_startdate", "date_startdateUTC", "date_starttime", "gender_code", "identifier", "jatosStudyResultId", "jatosVersion", "lang_code", "prolific_participant_id", "prolific_session_id", "prolific_study_id", "response", "response_clang", "screen_availableHeight", "screen_availableWidth", "screen_colorDepth", "screen_height", "screen_pixelDepth", "screen_screenX", "screen_screenY", "screen_width", "system_os", "test_file", "test_topic") %>% 
  write_csv(file = "CE_pilot_rawdata.csv")

```