---
title: "Preview demo test"
author: "Sau-Chin Chen"
date: "2023-1-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


- This pilot followed Bocanegra et al.(2022) EXP 2 and 3. 
- The participants were assumed the Taiwan residents.

## Script description

- Short = whole word on `cue_board`; blank on `interval_board`.
- Long 1 = whole word on `cue_board`; whole word on `interval_board`.
- Long 2 = component 1 on `cue_board`; component 2 on `interval_board`.

> whole word: "紅色方塊"
> component: "紅色","方塊“

## Data preview

```{r}
## Import data file. Use OsWEB transfer json to csv.
df <- read_csv(file="jatos_results_20230110070512.csv")  # pilot data 20230103
#df <- read_csv(file="jatos_results_20221226013035.csv")  # pilot data 20221226
#df <- read_csv(file="jatos_results_20221017061639.csv")  # pilot data 20221003
#df <- read_csv(file="jatos_results_20220926070123.csv") # pilot data 20220919

# Retreive the available complete codes
df %>% select(identifier) %>% unique() %>% write_csv(file = "complete_code_20230110.csv")

## Blocks in a session
### consent_tc, Lang_Test, Prac, Exp, Post_tc

## Retrieve the response to consent form
consent_response <- df %>% select(Block, identifier, response)  %>% filter(Block == "consent_tc")

## Retrieve the responses of Language test; compute by-participant accuracy percentage
test_result <- df %>% select(Block, identifier, response, correct)  %>% filter(Block == "Lang_Test") %>% group_by(identifier) %>% summarise(Accuracy = 100*mean(correct))


## Retrieve the responses of experimental session
#df %>% filter(Block == "Prac") %>%
#   bind_cols(sequence = rep(1:40,10)) %>%
#   filter(sequence %in%(9:40)) %>%
df %>% filter(Block == "Exp") %>%
  group_by(jatosStudyResultId, Presentation_style, Trial_type) %>%
  summarise(Trial_N = n(), Acc = 100*mean(correct)) %>%
left_join(
#df %>% filter(Block == "Prac") %>%
#   bind_cols(sequence = rep(1:40,10)) %>%
#   filter(sequence %in%(9:40)) %>%
df %>% filter(Block == "Exp") %>%
  filter(correct == 1) %>%
  group_by(jatosStudyResultId, Presentation_style, Trial_type) %>%
  summarise(RT = mean(response_time)),
by = c("jatosStudyResultId","Presentation_style","Trial_type")
) %>%
  group_by(Presentation_style, Trial_type) %>%
  summarise(N= n(), mRT = mean(RT), sdRT = sd(RT), Accuracy = mean(Acc))

#  summarise(n = n())
```

`r knitr::kable(consent_response)`

`r knitr::kable(test_result)`