---
title: "MH et al. (2021) Results verification"
author: "Sau-Chin Chen"
date: "2022/3/2"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	error = TRUE
)
library(tidyverse)

# Import the original results 
orig_results <- read_csv("orig_data/Data from all experiments in study is color continuously activated in a changing discourse context.csv") %>%
  mutate(
    Subject = as.character(Subject),
    List = as.factor(List),
    FirstorSecond = as.factor(FirstorSecond),
    Experiment = as.factor(Experiment)
  )
```

We downloaded the summary data from the authors' [OSF](https://osf.io/emgya). The did not provide the meta data about the variables. We converted the category variables to factors.

# Data summary


`r codebook::codebook(orig_results)`


`FirsttoSecond` was not the variable in Experiment 3.

Averaged accuracy and mean response times were stored in wide table. In the below code, we compared the overall accuracy and the averaged condition accuracy. 

```{r Acc_check}
check_result <- orig_results %>%
  mutate(Acc_r = (SentenceBlankPictureGrayACC+SentenceBlankPictureColorACC+SentenceColorPictureColorACC+SentenceColorPictureGrayscaleACC)/4,
         ACC_check = (round(Accuracy,3) == round(Acc_r,3) )) %>%
  summarise(sum(ACC_check == FALSE))
```


# Convert data sheet

There were `r check_result` observations had unequal accuracy values. Thus we removed `Accuracy` before we convert the data sheet into long table.

```{r wide-to-long, include=FALSE}
orig_results_wide <- orig_results %>% 
  select(-ends_with("RT"),-Accuracy) %>%
  rename(SentenceColorPictureGrayACC = SentenceColorPictureGrayscaleACC) %>%
  pivot_longer(cols = SentenceBlankPictureGrayACC:SentenceColorPictureGrayACC 	,
               names_to = c("Sentence","Picture"),
               names_pattern = "Sentence(.*)Picture(.*)ACC",
               values_to = c("Accuracy"),
               names_transform = list(Sentence = as.factor,
                                      Picture = as.factor)) %>%
left_join(  
orig_results %>% 
  select(-ends_with("Acc"),-Accuracy) %>%
  pivot_longer(cols = SentenceBlankPictureGrayRT:SentenceColorPictureGrayRT 	,
               names_to = c("Sentence","Picture"),
               names_pattern = "Sentence(.*)Picture(.*)RT",
               values_to = c("RT"),
               names_transform = list(Sentence = as.factor,
                                      Picture = as.factor)),
  by = c("Subject","List","FirstorSecond","Experiment","Sentence","Picture")
)

write_csv(orig_results_wide, file="orig_data/data_wide.csv")

orig_sum <- orig_results_wide %>% group_by(Experiment, Sentence, Picture) %>% summarise(N = n(), RT = paste0(round(mean(RT)),"(",  round(sd(RT)), ")"), 
            Acc = paste0(round(mean(Accuracy),2),"(",round(sd(Accuracy),2),")"))
```

# Reproduced exploratory analyses

Below table reproduced the exploratory analyses of the three studies.

`r knitr::kable(orig_sum)`

The original paper reported the effect size of by-participant analyses only.

- Experiment 1, sentences referred to object color

```{r exp1_sen_color}
effectsize::cohens_d(RT ~ Picture, data = subset(orig_results_wide, Experiment == "1" & Sentence == "Color"), paired = TRUE)
```


- Experiment 1, sentences did not refer to object color

```{r exp1_sen_blank}
effectsize::cohens_d(RT ~ Picture, data = subset(orig_results_wide, Experiment == "1" & Sentence == "Blank"), paired = TRUE)
```


- Experiment 2, sentences referred to object color

```{r exp2_sen_color}
effectsize::cohens_d(RT ~ Picture, data = subset(orig_results_wide, Experiment == "2" & Sentence == "Color"), paired = TRUE)
```

- Experiment 2, sentences did not refer to object color

```{r exp2_sen_blank}
effectsize::cohens_d(RT ~ Picture, data = subset(orig_results_wide, Experiment == "2" & Sentence == "Blank"), paired = TRUE)
```


- Experiment 3, sentences referred to object color

```{r exp3_sen_color}
effectsize::cohens_d(RT ~ Picture, data = subset(orig_results_wide, Experiment == "3" & Sentence == "Color"), paired = TRUE)
```

- Experiment 3, sentences did not refer to object color

```{r exp3_sen_blank}
effectsize::cohens_d(RT ~ Picture, data = subset(orig_results_wide, Experiment == "3" & Sentence == "Blank"), paired = TRUE)
```

# 