---
title: "Replication Pilot Summary"
author: "Sau-Chin Chen"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
```


> Pilot 1 and 2 had 10 participants to test the replication scripts.
> Pilot 3 was the formal replication test, but the number of participants reached 50% of our target sample size.

## Pilot 1

- This pilot followed Bocanegra et al.(2022) EXP 3. 
- We recruited 10 `Prolific` participants to test the feasibility of the experimental procedure.

- gap: n = "long cue"; y = "short cue"

```{r pilot_1, echo=TRUE}
df <- read_csv(file="jatos_results_20220926070123.csv") # pilot data 20220919

#df %>% filter(Block == "Prac") %>%
#   bind_cols(sequence = rep(1:40,10)) %>%
#   filter(sequence %in%(9:40)) %>%
df %>% filter(Block == "EXP") %>%
  group_by(jatosStudyResultId, gap, Trial_type) %>%
  summarise(Trial_N = n(), Acc = mean(correct)) %>%
left_join(
#df %>% filter(Block == "Prac") %>%
#   bind_cols(sequence = rep(1:40,10)) %>%
#   filter(sequence %in%(9:40)) %>%
df %>% filter(Block == "EXP") %>%
  filter(correct == 1) %>%
  group_by(jatosStudyResultId, gap, Trial_type) %>%
  summarise(RT = mean(response_time)),
by = c("jatosStudyResultId","gap","Trial_type")
) %>%
  group_by(gap, Trial_type) %>%
  summarise(N =  n(), mRT = mean(RT), sdRT = sd(RT), Accuracy = mean(Acc))
```

## Pilot 2

- This pilot followed Bocanegra et al.(2022) EXP 3, but dual feature/long cue used EXP 2 setting. There were missing labels in this script.
- We recruited 10 `Prolific` participants to test the feasibility of the experimental procedure.

- gap: n = "sequential"; y = "short cue"

```{r pilot_2, echo=TRUE}
df <- read_csv(file="jatos_results_20221017061639.csv")  # pilot data 20221003
#df <- read_csv(file="jatos_results_20220926070123.csv") # pilot data 20220919

df %>% filter(Block == "Prac") %>%
   bind_cols(sequence = rep(1:40,10)) %>%
   filter(sequence %in%(9:40)) %>%
#df %>% filter(Block == "EXP") %>%
  group_by(jatosStudyResultId, gap, Trial_type) %>%
  summarise(Trial_N = n(), Acc = mean(correct)) %>%
left_join(
df %>% filter(Block == "Prac") %>%
   bind_cols(sequence = rep(1:40,10)) %>%
   filter(sequence %in%(9:40)) %>%
#df %>% filter(Block == "EXP") %>%
  filter(correct == 1) %>%
  group_by(jatosStudyResultId, gap, Trial_type) %>%
  summarise(RT = mean(response_time)),
by = c("jatosStudyResultId","gap","Trial_type")
) %>%
  group_by(gap, Trial_type) %>%
  summarise(N = n(), mRT = mean(RT), sdRT = sd(RT), Accuracy = mean(Acc))

#  summarise(n = n())
```

## Pilot 3


- This pilot followed Bocanegra et al.(2022) EXP 2 and 3. 
- The participants were assumed the Taiwan residents.

### Script description

- Short = **short cue** whole word on `cue_board`; blank on `interval_board`.
- Long 1 = **long cue**, whole word on `cue_board`; whole word on `interval_board`.
- Long 2 = **sequential**, component 1 on `cue_board`; component 2 on `interval_board`.

> whole word: "紅色方塊"(red square)
> component: "紅色"(red),"方塊“(square)

- Trial type： "dual" = dual features; "single" = single feature.

- There were 35 participants collected.

```{r pilot_3, echo=TRUE}
## Import data file. Use OsWEB transfer json to csv.
df <- read_csv(file="jatos_results_20230110070512.csv")  # pilot data 20230103
#df <- read_csv(file="jatos_results_20221226013035.csv")  # pilot data 20221226
#df <- read_csv(file="jatos_results_20221017061639.csv")  # pilot data 20221003
#df <- read_csv(file="jatos_results_20220926070123.csv") # pilot data 20220919

# Retreive the available complete codes
#df %>% select(identifier) %>% unique() %>% write_csv(file = "complete_code_20230110.csv")

## Blocks in a session
### consent_tc, Lang_Test, Prac, Exp, Post_tc

## Retrieve the response to consent form
#consent_response <- df %>% select(Block, identifier, response)  %>% filter(Block == "consent_tc")

## Retrieve the responses of Language test; compute by-participant accuracy percentage
#test_result <- df %>% select(Block, identifier, response, correct)  %>% filter(Block == "Lang_Test") %>% group_by(identifier) %>% summarise(Accuracy = 100*mean(correct))


## Retrieve the responses of experimental session
#df %>% filter(Block == "Prac") %>%
#   bind_cols(sequence = rep(1:40,10)) %>%
#   filter(sequence %in%(9:40)) %>%
df %>% filter(Block == "Exp") %>%
  group_by(jatosStudyResultId, Presentation_style, Trial_type) %>%
  summarise(Trial_N = n(), Acc = 100*mean(correct)) %>%
left_join(
#df %>% filter(Block == "Prac") %>%
#   bind_cols(sequence = rep(1:40,10)) %>%
#   filter(sequence %in%(9:40)) %>%
df %>% filter(Block == "Exp") %>%
  filter(correct == 1) %>%
  group_by(jatosStudyResultId, Presentation_style, Trial_type) %>%
  summarise(RT = mean(response_time)),
by = c("jatosStudyResultId","Presentation_style","Trial_type")
) %>%
  group_by(Presentation_style, Trial_type) %>%
  summarise(N= n(), mRT = mean(RT), sdRT = sd(RT), Accuracy = mean(Acc))

#  summarise(n = n())
```
